\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2016-08-18 journalSwarmControl/SwarmControlIJRR.tex
Added swarm to keywords
added ayanian
shortened section names

@@

\keywords{micro-robot, global control, human-swarm interaction}

@@

\begin{dci}
The Authors declare that there is no conflict of interest.
To typeset a "Declaration of
  conflicting interests" section.
\end{dci}
\begin{funding}
%RULES: http://www.nsf.gov/pubs/policydocs/pappguide/nsf16001/aag_6.jsp
This work was supported by the National Science Foundation under Grant No.\ 
\href{http://nsf.gov/awardsearch/showAward?AWD_ID=1553063}{ [IIS-1553063]}.
\end{funding}
\begin{sm}
Video 1:  
Video 2: 
\end{sm}

>>>>

% How many words:  $ detex IJRRensembleDifferentialDrive.tex | wc -w

@@

\keywords{micro-robot, global control, swarm, human-swarm interaction}

@@

\begin{dci}
The Authors declare that there is no conflict of interest.
\end{dci}
\begin{funding}
%RULES: http://www.nsf.gov/pubs/policydocs/pappguide/nsf16001/aag_6.jsp
This work was supported by the National Science Foundation under Grant No.\ 
\href{http://nsf.gov/awardsearch/showAward?AWD_ID=1553063}{ [IIS-1553063]}.
\end{funding}
\begin{sm}
\begin{itemize}
\item Video 1: hardware experiments of object manipulation with a swarm of 100 kilobots.
\item Video 2:  simulation of parameter sweeps with swarm of robots manipulating objects.
\end{itemize}
\end{sm}

### 2016-08-18 journalSwarmControl/realExperiment.tex
changed position of overpic
shortened section names

\begin{figure}
\begin{center}
	\begin{overpic}[width=1.0\columnwidth]{RealMean}\put(42,20){\emph{t}= 90 s}\put(72,20){\emph{t}= 175 s}\end{overpic}
%	\begin{overpic}[width=0.35\columnwidth]{XYMeanControl.eps}\end{overpic}
\end{center}
\vspace{-1em}
\caption{\label{fig:realMean}
Regulating mean $x$ position of 100 kilobots using control law \eqref{eq:PDcontrolPosition}.
%Mean control plot with kilobots. %\todo{place a red star and a red circle at two spots on graph, put two images of the swar at right with a red star and red circle in left hand corner of these, and put a scale bar in image}
}
\end{figure}

\subsection{Automated object manipulation (hardware experiment)}

The kilobots performed five successful runs of object manipulation through the obstacle maze.
Each trial used 100 kilobots. Videos of each are in the multimedia extension. Trials two-five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  {\sc Matlab} code for vision processing, the policy iteration of \S \ref{subsec:objectpolicy} and the algorithm of \S \ref{sec:AlgObjectManipulation} is available on {\sc Matlab} Central by \cite{Shahrokhi2015MDP}.
Trials were run until the object COM entered the goal region.  The trials ran for \{1465, 3457, 3000, 2162, 2707\} s.  This is $2558\pm771$ s (mean$\pm$std). 
A circular object completed in 3155 s. 
A square object completed in 6871 s. 
\todo{A triangular object completed in ??:?? minutes.}

@@

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,29){\emph{t} = 3 s}\put(38,29){\emph{t} = 410 s}\put(70,29){\emph{t} = 710 s}
%\put(15,22){\emph{t} = 1374 s}\put(49,22){\emph{t} = 2185 s}\put(83,22){\emph{t} = 2703 s}
%\end{overpic}
\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,80){\emph{t} = 3 s}\put(38,80){\emph{t} = 410 s}\put(70,80){\emph{t} = 710 s}
\put(15,8){\emph{t} = 1374 s}\put(49,8){\emph{t} = 2185 s}\put(83,8){\emph{t} = 2703 s}
\end{overpic}
\vspace{-1em}
\caption{\label{fig:expSnapShot}{Snapshots showing the object manipulation experiment with 100 kilobots under automatic control. The automatic controller classifies pink objects as obstacles and generates a policy to the goal. See  video in multimedia extension.}
%\vspace{-2em}
}
\end{figure}

>>>>

\begin{figure}
\begin{center}
	\begin{overpic}[width=1.0\columnwidth]{RealMean}\put(6,30){\emph{t}= 90 s}\put(55,30){\emph{t}= 175 s}\end{overpic}
%	\begin{overpic}[width=0.35\columnwidth]{XYMeanControl.eps}\end{overpic}
\end{center}
\vspace{-1em}
\caption{\label{fig:realMean}
Regulating mean $x$ position of 100 kilobots using control law \eqref{eq:PDcontrolPosition}.
%Mean control plot with kilobots. %\todo{place a red star and a red circle at two spots on graph, put two images of the swar at right with a red star and red circle in left hand corner of these, and put a scale bar in image}
}
\end{figure}

\subsection{Automated object manipulation (hardware~experiment)}

The kilobots performed five successful runs of object manipulation through the obstacle maze.
Each trial used 100 kilobots. Videos of each are in the multimedia extension. Trials two-five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  {\sc Matlab} code for vision processing, the policy iteration of \S \ref{subsec:objectpolicy} and the algorithm of \S \ref{sec:AlgObjectManipulation} is available on {\sc Matlab} Central by \cite{Shahrokhi2015MDP}.
Trials were run until the object COM entered the goal region.  The trials ran for \{1465, 3457, 3000, 2162, 2707\} s.  This is $2558\pm771$ s (mean$\pm$std). 
A circular object completed in 3155 s. 
A square object completed in 6871 s. 
Three equilateral triangular objects of varying sizes failed in a total of seven runs.  Failures occurred when the object was pushed into a corner, requiring torque to be unstuck.  This paper focuses on force, but not torque control. Swarm torque control is the subject of ongoing research in \cite{Shahrokhi2016CASE}.

@@

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,29){\emph{t} = 3 s}\put(38,29){\emph{t} = 410 s}\put(70,29){\emph{t} = 710 s}
%\put(15,22){\emph{t} = 1374 s}\put(49,22){\emph{t} = 2185 s}\put(83,22){\emph{t} = 2703 s}
%\end{overpic}
\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,80){\emph{t} = 3 s}\put(38,80){\emph{t} = 410 s}\put(70,80){\emph{t} = 710 s}
\put(15,8){\emph{t} = 1374 s}\put(48,8){\emph{t} = 2185 s}\put(80,8){\emph{t} = 2703 s}
\end{overpic}
\vspace{-1em}
\caption{\label{fig:expSnapShot}{Snapshots showing the object manipulation experiment with 100 kilobots under automatic control. The automatic controller classifies pink objects as obstacles and generates a policy to the goal. See  video in multimedia extension.}
%\vspace{-2em}
}
\end{figure}

### 2016-08-18 journalSwarmControl/theory.tex
shortened section names

\end{bmatrix} = \begin{bmatrix}
0 & 1 & \ldots & 0 & 0 \\
0 & 0 & \ldots& 0 & 0 \\
\vdots &  \vdots & \ddots & \vdots & \vdots \\
0 & 0  & \ldots & 0 & 1 \\
0 & 0 & \ldots& 0 & 0 
\end{bmatrix}  \begin{bmatrix}
x_{1}\\
\dot{x}_{1}\\
\vdots \\
x_{n}\\
\dot{x}_{n}
\end{bmatrix} + \begin{bmatrix}
0\\
1\\
\vdots\\
0\\
1
\end{bmatrix} u_x
\end{equation}
 However, just as with one robot, we can only control two states because the controllability matrix $\mathcal{C}_n$ has rank two:
\begin{equation}
\mathcal{C}_n=\left[ \begin{matrix} 
0\\
1\\
\vdots\\
0\\
1
\end{matrix}
\,\middle\vert\,
  \begin{matrix} 
1\\
0\\
\vdots\\
1\\
0
\end{matrix}
\,\middle\vert\,
\begin{matrix} 
0\\
0\\
\vdots\\
0\\
0
\end{matrix}
\,\middle\vert\,
\begin{matrix} 
0\\
0\\
\vdots\\
0\\
0
\end{matrix}\,\middle\vert\,
\ldots \right], \quad \textrm{rank}(\mathcal{C}_n)=2.
\end{equation}  
\subsection{Controlling the mean position of many robots}\label{sec:controlMeanPosition}
This means \emph{any} number of robots controlled by a global command have just two controllable states in each axis. We cannot arbitrarily control the position and velocity of two or more robots, but have options on which states to control.  One option is to control the position and velocity of the $j^{th}$ robot. To find a potentially more useful option, we create the following reduced order system that represents the mean $x$ position and velocity of the $n$ robots:
\begin{align}
\begin{bmatrix}\nonumber
\dot{\bar{x}} \\
\ddot{\bar{x}}
\end{bmatrix} &= \frac{1}{n} \begin{bmatrix}
0& 1& \ldots &0& 1 \\
0& 0& \ldots &0& 0
\end{bmatrix}
\begin{bmatrix}
x_{1}\\
\dot{x}_{1}\\
\vdots\\
x_{n}\\
\dot{x}_{n}
\end{bmatrix} \\
&+ \frac{1}{n}\begin{bmatrix}
0& 0&  \ldots &0& 0 \\
0& 1&  \ldots &0& 1
\end{bmatrix}\begin{bmatrix} 
0\\
1\\
\vdots\\
0\\
1
\end{bmatrix} u_x
\end{align}
Thus:
\begin{equation}
\begin{bmatrix}
\dot{\bar{x}} \\
\ddot{\bar{x}}
\end{bmatrix} = \begin{bmatrix}
0& 1 \\
0& 0
\end{bmatrix}
\begin{bmatrix}
\bar{x}\\
\dot{\bar{x}}
\end{bmatrix} + \begin{bmatrix} 
0\\
1
\end{bmatrix} u_x
\end{equation}

@@

\subsection{Controlling the variance of many robots}\label{sec:VarianceControl}

@@

\subsection{Controlling both mean and variance of many robots}

>>>>

\end{bmatrix} = \begin{bmatrix}
0 & 1 & \ldots & 0 & 0 \\
0 & 0 & \ldots& 0 & 0 \\
\vdots &  \vdots & \ddots & \vdots & \vdots \\
0 & 0  & \ldots & 0 & 1 \\
0 & 0 & \ldots& 0 & 0 
\end{bmatrix}  \begin{bmatrix}
x_{1}\\
\dot{x}_{1}\\
\vdots \\
x_{n}\\
\dot{x}_{n}
\end{bmatrix} + \begin{bmatrix}
0\\
1\\
\vdots\\
0\\
1
\end{bmatrix} u_x
\end{equation}
 However, just as with one robot, we can only control two states because the controllability matrix $\mathcal{C}_n$ has rank two:
\begin{equation}
\mathcal{C}_n=\left[ \begin{matrix} 
0\\
1\\
\vdots\\
0\\
1
\end{matrix}
\,\middle\vert\,
  \begin{matrix} 
1\\
0\\
\vdots\\
1\\
0
\end{matrix}
\,\middle\vert\,
\begin{matrix} 
0\\
0\\
\vdots\\
0\\
0
\end{matrix}
\,\middle\vert\,
\begin{matrix} 
0\\
0\\
\vdots\\
0\\
0
\end{matrix}\,\middle\vert\,
\ldots \right], \quad \textrm{rank}(\mathcal{C}_n)=2.
\end{equation}  
\subsection{Controlling the mean position}\label{sec:controlMeanPosition}
This means \emph{any} number of robots controlled by a global command have just two controllable states in each axis. We cannot arbitrarily control the position and velocity of two or more robots, but have options on which states to control.  One option is to control the position and velocity of the $j^{th}$ robot. To find a potentially more useful option, we create the following reduced order system that represents the mean $x$ position and velocity of the $n$ robots:
\begin{align}
\begin{bmatrix}\nonumber
\dot{\bar{x}} \\
\ddot{\bar{x}}
\end{bmatrix} &= \frac{1}{n} \begin{bmatrix}
0& 1& \ldots &0& 1 \\
0& 0& \ldots &0& 0
\end{bmatrix}
\begin{bmatrix}
x_{1}\\
\dot{x}_{1}\\
\vdots\\
x_{n}\\
\dot{x}_{n}
\end{bmatrix} \\
&+ \frac{1}{n}\begin{bmatrix}
0& 0&  \ldots &0& 0 \\
0& 1&  \ldots &0& 1
\end{bmatrix}\begin{bmatrix} 
0\\
1\\
\vdots\\
0\\
1
\end{bmatrix} u_x
\end{align}
Thus:
\begin{equation}
\begin{bmatrix}
\dot{\bar{x}} \\
\ddot{\bar{x}}
\end{bmatrix} = \begin{bmatrix}
0& 1 \\
0& 0
\end{bmatrix}
\begin{bmatrix}
\bar{x}\\
\dot{\bar{x}}
\end{bmatrix} + \begin{bmatrix} 
0\\
1
\end{bmatrix} u_x
\end{equation}

@@

\subsection{Controlling the variance}\label{sec:VarianceControl}

@@

\subsection{Controlling both mean and variance}
